---
title: "Final Project - Is crime decreasing in the US according to the FBI Uniform Crime Reporting (UCR) Program"
author: "Dmitriy Burtsev"
output:
  slidy_presentation:
    incremental: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load library
```{r}
library(tidyverse)
library(htmltab)
```


## Acquire dataset from web to dataframe
*The FBI collects these data through the Uniform Crime Reporting (UCR) Program.*
Crime in the United States, by Volume and Rate per 100,000 Inhabitants, 1997–2016
Violent crime includes the offenses of murder and nonnegligent manslaughter, rape (legacy definition), robbery, and aggravated assault. Property crime includes the offenses of burglary, larceny-theft, and motor vehicle theft. 
The UCR Program does not have sufficient data to estimate for arson.
```{r}
url <- "https://ucr.fbi.gov/crime-in-the-u.s/2016/crime-in-the-u.s.-2016/topic-pages/tables/table-1"
dfrm = htmltab(doc = url, which = 1,rm_nodata_cols = F)
class(dfrm)
```
## Convert R data frame to tibble
I have to convert the original R data frame to Tibble data frame because our column names have spaces.
```{r}
df = as_tibble(dfrm)
class(df)
```

## Get the structure of the data frame.
Function str Compactly Display the Structure of an Arbitrary R Object
```{r}
str(df)
```

## Data clean up and transformations - Remove Rows with NA
Show the number of NA’s in each column of the data frame 
```{r}
colSums(is.na(df))
```
## There are two colums with NA: Rape(revised definition) and Rape(revised definition) rate
We should remove colums with NA
```{r}
df = select(df, -c(`Rape(revised definition)`,`Rape(revised definition) rate`))
str(df)
```


## All colums in dataframe are string. We should change some to integers or numbers
```{r}
df[["Year"]] = as.integer(df[["Year"]])
df[["Population"]] = as.integer(gsub(",", "", df[["Population"]], fixed = TRUE))
df[["Violentcrime"]] = as.integer(gsub(",", "", df[["Violentcrime"]], fixed = TRUE))
df[["Violent crime rate"]] = as.numeric(df[["Violent crime rate"]])
df[["Murder andnonnegligent manslaughter"]] = as.integer(gsub(",", "", df[["Murder andnonnegligent manslaughter"]], fixed = TRUE))
df[["Murder and nonnegligent manslaughter rate"]] = as.numeric(df[["Murder and nonnegligent manslaughter rate"]])
df[["Rape(legacy definition)"]] = as.integer(gsub(",", "", df[["Rape(legacy definition)"]], fixed = TRUE))
df[["Rape(legacy definition) rate"]] = as.numeric(df[["Rape(legacy definition) rate"]])
df[["Robbery"]] = as.integer(gsub(",", "", df[["Robbery"]], fixed = TRUE))
df[["Robbery rate"]] = as.numeric(df[["Robbery rate"]])
df[["Aggravated assault"]] = as.integer(gsub(",", "", df[["Aggravated assault"]], fixed = TRUE))
df[["Aggravated assault rate"]] = as.numeric(df[["Aggravated assault rate"]])
df[["Property crime"]] = as.integer(gsub(",", "", df[["Property crime"]], fixed = TRUE))
df[["Property crime rate"]] = as.numeric(gsub(",", "", df[["Property crime rate"]], fixed = TRUE))
df[["Burglary"]] = as.integer(gsub(",", "", df[["Burglary"]], fixed = TRUE))
df[["Burglary rate"]] = as.numeric(df[["Burglary rate"]])
df[["Larceny-theft"]] = as.integer(gsub(",", "", df[["Larceny-theft"]], fixed = TRUE))
df[["Larceny-theft rate"]] = as.numeric(gsub(",", "", df[["Larceny-theft rate"]], fixed = TRUE))
df[["Motor vehicle theft"]] = as.integer(gsub(",", "", df[["Motor vehicle theft"]], fixed = TRUE))
df[["Motor vehicle theft rate"]] = as.numeric(df[["Motor vehicle theft rate"]])
```
## Create a table directly from R Markdown
```{r}
knitr::kable(df, caption = 'Crime in the United States')
```

## Summary of Data in Data Frame
The statistical summary and nature of the data can be obtained by applying summary() function
```{r}
print(summary(df))  
```

## Pivot Year and Violentcrime columns from dataFrame
```{r}
df_year_violent = select(df, Year, Violentcrime)
tbl2 = df_year_violent %>% pivot_wider(names_from = Year, values_from = c(Violentcrime))
knitr::kable(tbl2, caption = 'Crime in the United States by Year')
```

## Statistical analysys

```{r}
ggplot(data = df, aes(x=Year)) + geom_point(aes(y = `Violent crime rate`, color = "Violent crime rate")) + 
geom_point(aes(y = `Murder and nonnegligent manslaughter rate`, color = "Murder and nonnegligent manslaughter rate")) +
geom_point(aes(y = `Rape(legacy definition) rate`, color = "Rape(legacy definition) rate")) +
geom_point(aes(y = `Robbery rate`, color = "Robbery rate")) +
geom_point(aes(y = `Aggravated assault rate`, color = "Aggravated assault rate")) + 
geom_point(aes(y = `Property crime rate`, color = "Property crime rate")) +
geom_point(aes(y = `Burglary rate`, color = "Burglary rate")) +  
geom_point(aes(y = `Larceny-theft rate`, color = "Larceny-theft rate")) +
geom_point(aes(y = `Motor vehicle theft rate`, color = "Motor vehicle theft rate"))  
```

## I visualize the results of your simple linear regression.
Add the regression line using geom_smooth() and typing in lm as  method for creating the line.
I used linear regression.
```{r}
df.graph<-ggplot(df, aes(x = Year, y=`Violent crime rate`)) + geom_point() + geom_smooth(method="lm", col="black")
df.graph
```

## Conclusion

Violent crime is decreasing over the years (1997-2016). We have a lover Rate
per 100,000 Inhabitants in 2016 than in 1997. There is a small increase in crime from 2014 to 2016.
Unfortunately FBI doesn't publish the data belong the 2016 year.
