---
title: "Week10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load library

```{r }
library(tidytext)
library(janeaustenr)
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(wordcloud)
library(reshape2)
```

### The function get_sentiments() allows us to get specific sentiment lexicons with the appropriate measures for each one.
```{r}
get_sentiments("afinn")
```
```{r}
get_sentiments("bing")
```
```{r}
get_sentiments("nrc")
```

### Sentiment analysis with inner join
*With data in a tidy format, sentiment analysis can be done as an inner join. This is another of the great successes of viewing text mining as a tidy data analysis task; much as removing stop words is an antijoin operation, performing sentiment analysis is an inner join operation.*
```{r}
tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)
```

*Now that the text is in a tidy format with one word per row, we are ready to do the sentiment analysis. First, let’s use the NRC lexicon and filter() for the joy words. Next, let’s filter() the data frame with the text from the books for the words from Emma and then use inner_join() to perform the sentiment analysis.*
```{r}
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
```
*Small sections of text may not have enough words in them to get a good estimate of sentiment while really large sections can wash out narrative structure. For these books, using 80 lines works well, but this can vary depending on individual texts, how long the lines were to start with, etc. We then use pivot_wider() so that we have negative and positive sentiment in separate columns, and lastly calculate a net sentiment (positive - negative).*
```{r}
jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```
*Now we can plot these sentiment scores across the plot trajectory of each novel. Notice that we are plotting against the index on the x-axis that keeps track of narrative time in sections of text.*
```{r}
ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```

### Comparing the three sentiment dictionaries
*Let’s use all three sentiment lexicons and examine how the sentiment changes across the narrative arc of Pride and Prejudice. First, let’s use filter() to choose only the words from the one novel we are interested in.*
```{r}
pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")

pride_prejudice
```
*Let’s again use integer division (%/%) to define larger sections of text that span multiple lines, and we can use the same pattern with count(), pivot_wider(), and mutate() to find the net sentiment in each of these sections of text.*
```{r}
afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
  pride_prejudice %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  pride_prejudice %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```
*We now have an estimate of the net sentiment (positive - negative) in each chunk of the novel text for each sentiment lexicon. Let’s bind them together and visualize them*
```{r}
bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```

*The three different lexicons for calculating sentiment give results that are different in an absolute sense but have similar relative trajectories through the novel.
Let’s look briefly at how many positive and negative words are in these lexicons.*
```{r}
get_sentiments("nrc") %>% 
  filter(sentiment %in% c("positive", "negative")) %>% 
  count(sentiment)
```
```{r}
get_sentiments("bing") %>% 
  count(sentiment)
```

### Most common positive and negative words

```{r}
bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts
```
```{r}
bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```
*the word “miss” is coded as negative but it is used as a title for young, unmarried women in Jane Austen’s works. If it were appropriate for our purposes, we could easily add “miss” to a custom stop-words list using bind_rows(). We could implement that with a strategy such as this.*
```{r}
custom_stop_words <- bind_rows(tibble(word = c("miss"),  
                                      lexicon = c("custom")), 
                               stop_words)

custom_stop_words
```
### Wordclouds
```{r}
tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```

*In other functions, such as comparison.cloud(), you may need to turn the data frame into a matrix with reshape2’s acast()*
```{r}
library(reshape2)

tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```

### Looking at units beyond just words
```{r}
p_and_p_sentences <- tibble(text = prideprejudice) %>% 
  unnest_tokens(sentence, text, token = "sentences")
p_and_p_sentences$sentence[2]
```
```{r}
austen_chapters <- austen_books() %>%
  group_by(book) %>%
  unnest_tokens(chapter, text, token = "regex", 
                pattern = "Chapter|CHAPTER [\\dIVXLC]") %>%
  ungroup()

austen_chapters %>% 
  group_by(book) %>% 
  summarise(chapters = n())
```

*Let’s make a data frame of how many words are in each chapter so we can normalize for the length of chapters. Then, let’s find the number of negative words in each chapter and divide by the total words in each chapter. For each book, which chapter has the highest proportion of negative words?*
```{r}
bingnegative <- get_sentiments("bing") %>% 
  filter(sentiment == "negative")

wordcounts <- tidy_books %>%
  group_by(book, chapter) %>%
  summarize(words = n())

tidy_books %>%
  semi_join(bingnegative) %>%
  group_by(book, chapter) %>%
  summarize(negativewords = n()) %>%
  left_join(wordcounts, by = c("book", "chapter")) %>%
  mutate(ratio = negativewords/words) %>%
  filter(chapter != 0) %>%
  slice_max(ratio, n = 1) %>% 
  ungroup()
```

## Extending analysis to new corpus and new lexicon
### What books are available in a tidy data frame of Jane Austen's novels?
```{r}
austen_books() %>% group_by(book) %>%
     summarise(total_lines = n())
```

### Lets use loughran lexicon with Persuasion book
*Check loughran lexicon*
```{r}
get_sentiments("loughran")

get_sentiments("loughran") %>% 
  filter(sentiment %in% c("positive", "negative")) %>% 
  count(sentiment)
```


```{r}
loughran_negative <- get_sentiments("loughran") %>% 
  filter(sentiment == "negative")

tidy_books %>%
  filter(book == "Persuasion") %>%
  inner_join(loughran_negative) %>%
  count(word, sort = TRUE)
```
### Get Persuasion book
```{r}
Persuasion = tidy_books %>% 
  filter(book == "Persuasion")

Persuasion
```

### Use mutate() to find the net sentiment in each of these sections of text.
```{r}
loughran <- Persuasion %>% 
  inner_join(get_sentiments("loughran")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  #summarise(sentiment = sum(value)) %>% 
  mutate(method = "loughran")
```
### Most common positive and negative words

```{r}
loughran_word_counts <- Persuasion %>%
  inner_join(get_sentiments("loughran")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

loughran_word_counts
```

### We can use ggplot2 to show this data visually
```{r}
loughran_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```

### Wordclouds
```{r}
Persuasion %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```

